Summary

### 2016-02-05 inst/examples/20151209-HelsinkiDH.Rmd
ok

```{r 20151209-HDH-toptopic, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
p1 <- top_plot(dfo, "subject_topic", 10) + ylab("Title count (n)") + ggtitle(paste("Top themes (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = ""))
print(p1)

p2 <- top_plot(df, "subject_topic", 10) + ylab("Title count (n)") + ggtitle(paste("Top themes (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = ""))
print(p2)
```

>>>>

```{r 20151209-HDH-toptopic, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
p1 <- top_plot(dfo, "topic", 10) + ylab("Title count (n)") + ggtitle(paste("Top themes (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = ""))
print(p1)

p2 <- top_plot(df, "topic", 10) + ylab("Title count (n)") + ggtitle(paste("Top themes (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = ""))
print(p2)
```

### 2016-02-05 inst/examples/summary.Rmd
ok

```{r missing, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}

library(stringr)
library(dplyr)
library(reshape2)
library(ggplot2)
ntop <- 20

@@

@@

```{r topics1, topics, echo=FALSE, message=FALSE, warning=FALSE}
# List all topics
spl <- strsplit(na.omit(as.character(df$subject_topic)), ";")

@@

Top-`r ntop` topics and number of documents for each. In total, there are `r length(unique(df$subject_topic))` unique topics and `r sum(!is.na(df$subject_topic))` documents assigned to one or more topics (`r round(100*mean(!is.na(df$subject_topic)))`).

```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
par(mar = c(5, 10, 3, 1)); barplot(rev(rev(sort(table(df$subject_topic)))[1:ntop]), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Most common topics")
```

>>>>

```{r missing, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
library(stringr)
library(dplyr)
library(reshape2)
library(ggplot2)
ntop <- 20

@@

Conversions from the original to preprocessed fields:

```{r summary-conversions, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
field.conversions <- cbind(harmonize_field_names(), preprocessed = unname(sapply(conversions, function (x) {paste(x, collapse = ";")})[as.character(harmonize_field_names()$name)]))
names(field.conversions) <- c("marc_clearname", "marc_field", "preprocessed_fields")
field.conversions <- field.conversions[, c(2, 1, 3)]
kable(field.conversions)
```

@@

```{r topics1, topics, echo=FALSE, message=FALSE, warning=FALSE}
# List all topics
spl <- strsplit(na.omit(as.character(df$topic)), ";")

@@

Top-`r ntop` topics and number of documents for each. In total, there are `r length(unique(df$topic))` unique topics and `r sum(!is.na(df$topic))` documents assigned to one or more topics (`r round(100*mean(!is.na(df$topic)))`).

```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
par(mar = c(5, 10, 3, 1)); barplot(rev(rev(sort(table(df$topic)))[1:ntop]), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Most common topics")
```
